Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2020-04-21 WorkSpace/Paper/Paper.tex
updated model and experiment graphs

\subsection{PRNG Implementations}
\subsection{Predictive Network}
The predictor is a convolutional neural network implementing the function
: $P(r_{split}) \mathbb{B}$ 7→B(7)wherersplitis  the  generator’s  output  vector  with  the  last  element  removed.The  last  element  is  used  as  the  corresponding  label  for  the  predictor’s  input.
\begin{figure}[H]
\centering
\includegraphics[width=1\linewidth]{./Images/PredictiveModel.png}
\caption{Predictive Model}
\label{fig:globfig}
\end{figure}

\subsection{Experimental Setup}
\begin{figure}[H]
\centering
\includegraphics[width=1\linewidth]{./Images/ModelDiagram.png}
\caption{Experiment Model}
\label{fig:globfig}
\end{figure}

>>>>

\subsection{PRNG Implementations}
\subsection{Predictive Network}
NOTE THE Equation will have to be re-done and diagrams re-drawn to reflect our experiment.
The predictor is a convolutional neural network implementing the function ...
: $P(r_{split}) \mathbb{B}$ 7→B(7)wherersplitis  the  generator’s  output  vector  with  the  last  element  removed.The  last  element  is  used  as  the  corresponding  label  for  the  predictor’s  input.
\begin{figure}[H]
\centering
\includegraphics[width=1\linewidth]{./Images/PredictiveModel.png}
\caption{Predictive Model}
\label{fig:globfig}
\end{figure}

\subsection{Experimental Setup}
\begin{figure}[H]
\centering
\includegraphics[width=1\linewidth]{./Images/SimpleModel.png}
\caption{Experiment Model}
\label{fig:globfig}
\end{figure}

\subsection{Experimental Setup}
\begin{figure}[H]
\centering
\includegraphics[width=1\linewidth]{./Images/GranularModel.png}
\caption{Experiment Model}
\label{fig:globfig}
\end{figure}
